cardinalR: Generating interesting high-dimensional data structures

### 2025-04-26 paper-cardinalR.Rmd
Added Table 9

```{r}
add_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_bkgnoise",
                            "randomize_rows",
                            "gen_nproduct",
                            "gen_nsum",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3",
                            "gen_rotation",
                            "normalize_data"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
add_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_bkgnoise",
                            "randomize_rows",
                            "relocate_clusters",
                            "gen_nproduct",
                            "gen_nsum",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3",
                            "gen_rotation",
                            "normalize_data"), 
                        exp = c("Generates additional noise dimensions.",
                                "Adds background noise.",
                                "Randomizes the rows.",
                                "Relocates the clusters.",
                                "Generates a vector of positive integers whose product is approximately equal to a target value.",
                                "Generates a vector of positive integers whose summation is approximately equal to a target value.",
                                "Generates random noise dimensions with wavy pattern generated with theta.",
                                "Generates random noise dimensions with wavy pattern generated with power functions.",
                                "Generates random noise dimensions with wavy pattern generated with power and sine functions.",
                                "Generates rotations.",
                                "Normalizes data."))
```
